---
title: "Data 605 - Week12 DQ"
author: "Baron Curtin"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(warning = FALSE)

loadPkg <- function(x) {
  if(!require(x, character.only = T)) install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
  require(x, character.only = T)
}

libs <- c("knitr", "magrittr", "data.table", "kableExtra", "tidyverse", "matlib", "combinat", "leaps", "dummies")

lapply(libs, loadPkg)
```

## Question 1
Lets try to create a regression model that can predict college education based on a number of factors about a neighborhood in the Midwest

```{r}
data("midwest")
```

Create Dummy Variables
```{r}
cols <- c("state", "inmetro")

midwest2 <- midwest %>%
  select(-c("county", "PID", "category")) %>%
  select_at(vars(-matches("pop"))) %>%
  mutate_at(cols, as.factor) %>%
  as.data.frame() %>%
  dummy.data.frame(sep = ".")
```

Generate Model
```{r}
regDiags <- regsubsets(percollege ~ ., data = midwest2, method = "exhaustive", nvmax = NULL, nbest = 1, really.big = T)
diagSum <- summary(regDiags)
print(diagSum)
```


```{r}
# determine best fits
plot(diagSum$cp, xlab = "Number of Variables", ylab = "Cp")
points(which.min(diagSum$cp), diagSum$cp[which.min(diagSum$cp)], pch = 20, col = "red")

# cp plot
par(mfrow=c(1,2))
plot(regDiags, scale = "Cp", main = "Cp")

# r^2 splot
plot(regDiags, scale = "adjr2", main = "Adjusted R^2")
```

```{r}
model <- lm(percollege ~ . -state.WI -inmetro.0 - inmetro.1, data = midwest2)
summary(model)
```

Evaluation
```{r}
par(mfrow=c(2,2))

plot(model)
hist(model$residuals)
qqnorm(model$residuals)
qqline(model$residuals)
```

The diagnostics indicate that 3 variables (inmetro.0, inmetro.1, and state.WI) do not add more value to the model than they detract. As such, those three variables were left out of the model and at a ~.94 R^2, the model does a pretty good job at providing insight into whether a person was college educated or not. Analysis of the residuals does give the impression that there is significant clustering going on with the appearance of 3 distinct clusters.